---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r initial_setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(intendo)
library(dplyr)
library(lubridate)
```

# intendo

<!-- badges: start -->
<!-- badges: end -->

The goal of the **intendo** R package is to make it much easier to work with our own data. Here at Intendo.

## A Example of How to Use **intendo**

Get the appropriate environment variables set in your system (ask us how to do that). Then, you can make a connection to the database with `db_con()`

```{r connecting}
intendo <- db_con()
```

Then we can get access to a specific table, creating a `tbl_dbi` object:

```{r tbl_daily_users}

daily_users <- tbl_daily_users(con = intendo)
daily_users
```

Now with `daily_users` and a little **dplyr**, we can easily query the table for specific information.

```{r get_user_info}
daily_users %>%
  mutate(date = as.Date(time)) %>%
  filter(date == "2015-10-31", at_eoc == 1) %>%
  select(user_id, total_revenue) %>%
  group_by(user_id) %>%
  summarize(total_revenue = max(total_revenue, na.rm = TRUE)) %>%
  arrange(desc(total_revenue))
```

And this is only the beginning. The development team is working toward adding functions that get us our KPIs, help us generate reports, and much more.
