---
title: "Write R Code"
output:
  html_document:
    df_print: paged
---

```{r setup}
library(tidyverse)
```

## Your Turn 1

1. Re-write this ggplot2 theme as a function. Call it `theme_avalanche_h()`.

```{r}
library(ggplot2)

theme_minimal(base_size = 14) + 
  theme(panel.grid.minor = element_blank(), panel.grid.major.y = element_blank())
```

2. Run this code to test that your function works

```{r}
residents_per_sector <- 
  data.frame(
    sector = as.factor(1:8),
    residents = c(1000, 2034, 4594, 2304, 8093, 1200, 300, 2398)
  )

ggplot(residents_per_sector, aes(forcats::fct_reorder(sector, residents), residents)) +
  geom_col() + 
  coord_flip() + 
  xlab("sector") + 
  theme_avalanche_h()
```

## Your Turn 2

1. Create a new file with `use_r()` called "db_con"
2. Put this function in the file and save it:

```{r}
db_con <- function(dbname = "residents_per_sector") {
  dbname <- match.arg(dbname)
  # We will set up real database connections later. For now, we'll just return
  # some hard-coded data instead.
  data.frame(
    sector = as.factor(1:8),
    residents = c(1000, 2034, 4594, 2304, 8093, 1200, 300, 2398)
  )
}
```

3. Use `load_all()` to load the package function.
4. Run this code to make sure it works:


```{r}
ggplot(
  db_con(), 
  aes(forcats::fct_reorder(sector, residents), residents)
) +
  geom_col() + 
  coord_flip() + 
  xlab("sector") 
```


## Your Turn 3

1. Fix the code in `R/themes.R` to use `ggplot2::` instead of `library(ggplot2)`
2. Run `use_package("ggplot")` to add ggplot2 to `Imports`
3. Re-load the package (`Cmd/Ctrl+Shift+L`) and run this code to make sure it works:

```{r}
ggplot(
  db_con(), 
  aes(forcats::fct_reorder(sector, residents), residents)
) +
  geom_col() + 
  coord_flip() + 
  xlab("sector") +
  theme_avalanche()
```


## Your Turn 4

1. We need roxygen2 for this exercise. We'll learn more about it in the next module. For now, just run `use_roxygen_md()`
2. Run `use_tibble()` and `use_data_table()`
3. In `R/get_data.R`, edit the function to be able to return a data table: Add the argument `data_table = FALSE`. If `data_table` is `TRUE`, convert the data frame with `data.table::as.data.table()`
4. Run this code to make sure it works:

```{r}
res_data <- get_resident_data(data_table = TRUE)

stopifnot(data.table::is.data.table(res_data))

res_data
```

---

**Finish early? Try this stretch goal:**

Run `use_pipe()` to add the magrittr pipe to your package. What changed?

## Take-aways

* Add R files with `use_r()`; load the functions with `load_all()`; build the package with `build()`
* Import packages with `use_package()` and use the format `pkg::fun()` to call functions from other packages
* usethis has several functions for setting up common or complicated packages that you might want to include, such as tibbles and data tables, the pipe, or Rcpp and friends.

