---
title: "Setup R Packages"
output:
  html_document:
    df_print: paged
---

```{r setup}
library(usethis)
library(devtools)
library(desc)
```

## Your Turn 1

1. Load usethis and devtools if you haven't.

2. Open the DESCRIPTION file and take a look. It's very generic!

3. Run `edit_r_profile()`. Copy and paste this code into your R profile, but change it to your name and email. If you would like to add your ORCID ID see `?use_description` for an example for an example that includes that.

**If you don't want to change your R profile, you can just run the code in the console without running `edit_r_profile()` or restarting**

```{r}
options(
  usethis.description = list(
    `Authors@R` = 'person("First", "Last", email = "email@example.com", role = c("aut", "cre"))',
    License = "MIT + file LICENSE",
    Language =  "es"
  )
)
```

4. Then, restart your R session (Session > Restart R). 

5. When you've restarted, run `use_description()` to replace the DESCRIPTION file.

6. Open the DESCRIPTION file and take a look around.

**Finish early? Try this stretch goal:**

Read the help page for `use_usethis()`. If there are any of these that you'd like available in all interactive sessions, run the function to get the related code and add it to your R Profile. Then, restart your R session.

## Your Turn 2

1. Add a new author to `avalanchr` using `desc::desc_add_author()`. Set `given` to "Barret", `family` to "Wallace", and `role` to "aut". 

2. In DESCRIPTION, change the title to "Tools for the Avalanche Data Science Team"

3. Change the Description field to "A set of tools to use within the Avalance Data Science team. This package contains functions for connecting to data bases, R markdown templates, ggplot2 themes, and more."

4. Run `use_tidy_description()` to clean up the file. 

## Your Turn 3

1. Run `use_mit_license("AVALANCHE")`. What changed?

**Finish early? Try this stretch goal:**

Add "AVALANCHE" as an author with the role of copyright holder.

Change the license to use the proprietary license above.


## Take-aways

* devtools and usethis make your life a lot easier as a package developer!
* Use `create_package()` to create a new R package
* Include DESCRIPTION defaults in your R profile (`edit_r_profile()`) to auto-populate your information
* `use_*_license()` or use a proprietary license to create an appropriate license for your package
