---
title: "01_02_databases"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(DBI)
library(RMariaDB)
library(usethis)
```

## Working with Data in a Database, Part II

For this workshop we have a MySQL database available on AWS. I'll provide the necessary information about how to access it here. 

A safe way to store secrets on a system is to use environment variables. Let's use `usethis::edit_r_envion()` to add environment variables that contain configuration and authentication values for the `intendo` database.

``` r
# Edit the `.Renviron` file
edit_r_envion()
```

This is what the lines to be added should look like:

```
DBNAME=intendo
USERNAME=
PASSWORD=
HOST=intendo-db.csa7qlmguqrf.us-east-1.rds.amazonaws.com
PORT=3306
```

Let's make a connection to the database (i.e., create a `con` object):

```{r mysql_connection_to_db}
con <-
  DBI::dbConnect(
    drv = RMariaDB::MariaDB(),
    dbname = Sys.getenv("DBNAME"),
    username = Sys.getenv("USERNAME"),
    password = Sys.getenv("PASSWORD"),
    host = Sys.getenv("HOST"),
    port = Sys.getenv("PORT")
  )
```

To determine which tables are in the database, we can use the `DBI::dbListTables()` function. 

```{r list_tables}
DBI::dbListTables(con)
```

Those are the tables that the **intendo** organization uses on a daily basis. They contain all of the data on users' sessions (`daily_users`), any revenue generated (`revenue`), and summarized information on user history (`users`) for their one game called **Super Jetroid**.

## YOUR TURN, IT'S TIME TO CODE

Now, a thing to do (to enable data access to the data users in the org) is to write some functions. Here are the functions to write:

- One function that creates a connection object to the `intendo` database (*ans_01_02.1*)
- Three functions that create a `tbl_dbi` object for the three tables in a the `intendo` database (*ans_01_02.2*)

